---
title: "Homework 1"
author: "Kodiak Soled"
date: "9/20/2019"
output: github_document
---

**Problem 1**

```{r setup, include = FALSE}
library(tidyverse)
```

_Creating a Dataframe_

The following dataframe is comprised of a random sample size of 8 from a standard normal distribution, a logical vector whose elements of the sample are greater than 0, a character vector of length 8, and a factor vector of length 8 with 3 different factor "levels": 
```{r}
set.seed(100)
hw1_pb1_df = tibble(
  sample = rnorm(8, mean = 0, sd = 1), 
  vec_logical = c(sample > 0),
  vec_char = c("one", "two", "three", "four", "five", "six", "seven", "eight"),
  vec_factor = factor(c("low", "low", "low", "med", "med", "med", "high", "high"))
)
```

_Taking the Mean of Variables_

We can take the mean of the numeric vector (i.e., sample) and the logical vector (i.e., vec_logical) from the above dataframe using the following code:
```{r}
mean_samp = mean(pull(hw1_pb1_df, sample))
mean_vec_logical = mean(pull(hw1_pb1_df, vec_logical))
```
From this code, we can find: 

* The mean of the sample is `r mean(pull(hw1_pb1_df, sample))`.

* The mean of the vec_logical is `r mean(pull(hw1_pb1_df, vec_logical))`.

However, if we try to take the mean of a character (i.e., vec_char) or factor (i.e., vec_factor) vector, R will present a warning output stating that this function is not possible. This code would look like the following: 
```{r eval = FALSE}
mean_vec_char = mean(pull(hw1_pb1_df, vec_char))
mean_vec_factor = mean(pull(hw1_pb1_df, vec_factor))
```
