---
title: "Homework 1"
author: "Kodiak Soled"
date: "9/20/2019"
output: github_document
---

**Problem 1**

```{r setup, include = FALSE}
library(tidyverse)
```

_Creating a Dataframe_

The following dataframe is comprised of a random sample size of 8 from a standard normal distribution, a logical vector whose elements of the sample are greater than 0, a character vector of length 8, and a factor vector of length 8 with 3 different factor "levels": 
```{r}
set.seed(100)
hw1_pb1_df = tibble(
  sample = rnorm(8, mean = 0, sd = 1), 
  vec_logical = c(sample > 0),
  vec_char = c("one", "two", "three", "four", "five", "six", "seven", "eight"),
  vec_factor = factor(c("low", "low", "low", "med", "med", "med", "high", "high"))
)
```

_Taking the Mean of Variables_

We can take the mean of the numeric vector (i.e., sample) and the logical vector (i.e., vec_logical) from the above dataframe using the following code:
```{r}
mean_samp = mean(pull(hw1_pb1_df, sample))
mean_vec_logical = mean(pull(hw1_pb1_df, vec_logical))
```
From this code, we can find: 

* The mean of the sample is `r mean(pull(hw1_pb1_df, sample))`.

* The mean of the vec_logical is `r mean(pull(hw1_pb1_df, vec_logical))`.

However, if we try to take the mean of a character (i.e., vec_char) or factor (i.e., vec_factor) vector, R will present a warning output stating that this function is not possible. This code would look like the following: 
```{r eval = FALSE}
mean_vec_char = mean(pull(hw1_pb1_df, vec_char))
mean_vec_factor = mean(pull(hw1_pb1_df, vec_factor))
```

_Converting Variables_

When we convert a logical and factor variable into a numeric variable, we can yield a numeric output for each. However, when we convert a character variable into a numeric variable, the output shows NA's. This explains why we could not take the mean of this variable above. The code to convert these variables into a numeric variable would look like the following:   
```{r eval = FALSE}
as.numeric(pull(hw1_pb1_df, vec_factor))
as.numeric(pull(hw1_pb1_df, vec_logical))
as.numeric(pull(hw1_pb1_df, vec_char))
```

Since we just found we can convert a logical vector into a numeric vector, this allows us to then multiply our random sample by the result:
```{r}
#
vec_logical = as.numeric(pull(hw1_pb1_df, vec_logical)) 
vec_logical * (pull(hw1_pb1_df, sample))
```

Furthermore, we can also convert the logical vector into a factor vector. However, a factor vector cannot be multiplied and the output will again show NA's. Thus, we cannot multiple the factor vector by our random sample: 
```{r warning = FALSE}
vec_factor = as.factor(pull(hw1_pb1_df, vec_logical))
vec_factor * (pull(hw1_pb1_df, sample))
```

Nonetheless, by converting the logical vector into a factor vector and then into a numeric vector, now we can multiply the result by our random sample:
```{r}
vec_numeric = as.numeric(vec_factor) 
vec_numeric * (pull(hw1_pb1_df, sample))
```

**HW Problem 2**

_Creating a Dataframe_

This second dataframe is comprised of two random samples (x and y) of size 500 from a standard normal distribution, a logical vector that indicates whether x + y > 1, and the coerced numeric and factor vectors of the previous logical vector:
```{r}
set.seed(100)
hw1_pb2_df = tibble(
  x = rnorm(500, mean = 0, sd = 1),
  y = rnorm(500, mean = 0, sd = 1),
  vec_logical = c(x + y > 1),
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical)
)
```

_Describing the Dataframe_

* The dataset has `r nrow(hw1_pb2_df)*ncol(hw1_pb2_df)` variables (`r nrow(hw1_pb2_df)` rows and `r ncol(hw1_pb2_df)` columns). 
* The mean of x is `r mean(pull(hw1_pb2_df, x))`.
* The median of x is `r median(pull(hw1_pb2_df, x))`.
* The standard deviation of x is `r sd(pull(hw1_pb2_df, x))`.
* The proportion of cases where x + y > 1 is `r sum(pull(hw1_pb2_df, vec_logical), na.rm=TRUE)/500`.

The code that was used to find the above attributes about the second dataframe is as follows: 
```{r eval = FALSE}
nrow(hw1_pb2_df)*ncol(hw1_pb2_df)
mean(pull(hw1_pb2_df, x))
median(pull(hw1_pb2_df, x))
sd(pull(hw1_pb2_df, x))
sum(pull(hw1_pb2_df, vec_logical), na.rm=TRUE)/500
```

_Making Scatterplots of the Dataframe_ 

Below is a scatterplot of our two random samples x and y. The logical variable is colored with teal to indicate values where x + y > 1 and peach to indicate values where x + y <= 1:
```{r}
ggplot(hw1_pb2_df, aes(x = x, y = y, color = vec_logical)) + geom_point()
```

I will now export this scatterplot to my project directory using the following code: 
```{r}
ggsave("hw1_pb2_df.pdf", width = 4, height = 6)
```

This next scatterplot of our two random samples x and y is colored with a gradient of black to blue to represent the continuous nature of a numeric variable:
```{r}
ggplot(hw1_pb2_df, aes(x = x, y = y, color = vec_numeric)) + geom_point()
```

This last scatterplot of our two random samples x and y is similarly colored in the same fashion as the first scatterplot as a factor variable similarly uses categories to indicate which values are x + y > 1 and which values are x + y <= 1:
```{r}
ggplot(hw1_pb2_df, aes(x = x, y = y, color = vec_factor)) + geom_point()
```

_Comment on Color Scales_

In summary, the three scatterplot’s color scales represent the type of variable in each respective scatterplot. Thus, the first and third scatterplots (vec_factor and vec_logical) have two distinct colors that represents categorical data within a factor and logical vector. The second scatterplot (vec_numeric) has a gradient which represents continuous data of a numeric vector


